OptiFit: a fast method for fitting amplicon sequences to existing OTUs

### 2021-06-24 paper/paper.Rmd
Try setting seed in paper to make figure pdfs stop changing

```{r deps, message = FALSE}
library(cowplot)
library(glue)
library(here)
library(knitr)
library(schtools)
library(tidyverse)
snakemake <- params$snakemake
load(here(snakemake@input[['rda']]))
figures_meta <- yaml::read_yaml(here('config', 'figures.yaml'))
figs <- function(fig_name, attribute) {
  value <- figures_meta[[fig_name]][[attribute]]
  if (attribute == 'cap') {
    value <- glue("\\label{fig:[fig_name]}[value]", .open='[', .close = ']')
  } else {
    value <- eval(parse(text = value))
  }
  return(value)
}
```

>>>>

```{r deps, message = FALSE}
library(cowplot)
library(glue)
library(here)
library(knitr)
library(schtools)
library(tidyverse)
snakemake <- params$snakemake
load(here(snakemake@input[['rda']]))
figures_meta <- yaml::read_yaml(here('config', 'figures.yaml'))
figs <- function(fig_name, attribute) {
  value <- figures_meta[[fig_name]][[attribute]]
  if (attribute == 'cap') {
    value <- glue("\\label{fig:[fig_name]}[value]", .open='[', .close = ']')
  } else {
    value <- eval(parse(text = value))
  }
  return(value)
}
set.seed(20210624)
```
